Tree level scattering amplitude in (De)constructed gauge theory

### 2025-04-15 Intermediate report/main.tex
New

\documentclass{beamer}
\usetheme{Madrid}
\usefonttheme{professionalfonts}
\usecolortheme{rose}
\usepackage{fontspec}
\setmainfont{Times New Roman}
\usepackage{amsmath}
\usepackage{bm}
\usepackage{booktabs}
\usepackage{tikz}
\usepackage{svg}
\usepackage{graphics}
\usepackage{appendixnumberbeamer}
\usepackage{mathtools}
\usepackage{enumitem}
\usepackage{subcaption}
\usepackage{comment}
\usepackage[most]{tcolorbox}
\tcbset{
  thickitembox/.style={
    colback=white,
    colframe=white,
    left=2mm,
    before skip=4pt,
    after skip=4pt,
    borderline west={3pt}{0pt}{gray},  % ← 这里控制线条粗细和颜色
    enhanced,
  }
}
\setlist[itemize]{label=\textbullet}
\usetikzlibrary{decorations.pathreplacing}
\usetikzlibrary{arrows.meta}
\setlength{\parskip}{0.3em}
\newcommand{\aket}[1]{|#1\rangle}
\newcommand{\sket}[1]{|#1]}
\newcommand{\avg}[1]{\langle #1 \rangle}
\newcommand{\mdavg}[2]{\langle #1 \rangle\!\langle #2 \rangle}
\newcommand{\asqu}[1]{{\langle#1\rangle}^2}
\AtBeginSection[]{
\begin{frame} 
    \frametitle{Contents}
    \tableofcontents[currentsection]
\end{frame}
}
\title[Application of BCFW]{A complete solution for scattering in a kind of quiver gauge theory}
\author{Su Yingze}
\institute{Nagoya University}
\date[4 21st 2025]{April 21st 2025}

\begin{document}
\frame{\titlepage}
\section{Why we need new method?}
\begin{frame}
    \frametitle{Why we need new method?}
    Feynman diagram is a brilliant method without doubt, but it also faces many challenges.
    \begin{itemize}
        \item How to compute high multiplicity amplitudes, like n gluons scattering.
        \item Gauge redundancies bring us many structral complications and non-physical degrees of freedom.
        \item Some symmetries are hidden, like the dual superconformal symmetry for $\mathcal{N}=4$ SYM.
        \item Is the local field theory the most basic discription for physics?
    \end{itemize}
\end{frame}
\begin{frame}
    \frametitle{From Frynman diagram to On-shell method}
    On-shell here means that all quantities we use are gauge invariant and satisfy the on-shell condition.
    Specifically, there are many ingredients under this frame
    \begin{itemize}
        \item The analytic continuation for S-matrix.
        \item The color-ordered amplitudes.
        \item The BCFW recursion relation.
        \item The spinor helicity discription for amplitudes.
    \end{itemize}
\end{frame}
\section{Preliminary}
\begin{frame}
    \frametitle{A brief introduction to BCFW}
    BCFW recursion relation is a method to compute scattering amplitude recursively, means that you can 
    compute higher point amplitudes from lower point.
    \par
 \begin{itemize}[label=\textbullet]
    \item Ruth Britto
    \item Freddy Cachazo
    \item Bo Feng
    \item Edward Witten
 \end{itemize}

@@

%Flowchart: Connector [id:dp8833995378786028] 
\draw  [fill={rgb, 255:red, 153; green, 151; blue, 151 }  ,fill opacity=1 ] (100,151.75) .. controls (100,139.19) and (110.41,129) .. (123.25,129) .. controls (136.09,129) and (146.5,139.19) .. (146.5,151.75) .. controls (146.5,164.31) and (136.09,174.5) .. (123.25,174.5) .. controls (110.41,174.5) and (100,164.31) .. (100,151.75) -- cycle ;
%Straight Lines [id:da4824712234334869] 
\draw    (72.5,88.5) -- (107,134) ;
%Straight Lines [id:da012324134018845356] 
\draw    (146.5,151.75) -- (202.5,151.5) ;
%Straight Lines [id:da08630319677446052] 
\draw    (107,169.5) -- (74.5,207.5) ;
%Right Arrow [id:dp15563446404618686] 
\draw   (213,146.88) -- (234.3,146.88) -- (234.3,142) -- (248.5,151.75) -- (234.3,161.5) -- (234.3,156.63) -- (213,156.63) -- cycle ;
%Flowchart: Connector [id:dp3078703826898672] 
\draw  [fill={rgb, 255:red, 153; green, 151; blue, 151 }  ,fill opacity=1 ] (285,152.75) .. controls (285,140.19) and (295.41,130) .. (308.25,130) .. controls (321.09,130) and (331.5,140.19) .. (331.5,152.75) .. controls (331.5,165.31) and (321.09,175.5) .. (308.25,175.5) .. controls (295.41,175.5) and (285,165.31) .. (285,152.75) -- cycle ;
%Flowchart: Connector [id:dp8700788921830469] 
\draw  [fill={rgb, 255:red, 153; green, 151; blue, 151 }  ,fill opacity=1 ] (385,153.75) .. controls (385,141.19) and (395.41,131) .. (408.25,131) .. controls (421.09,131) and (431.5,141.19) .. (431.5,153.75) .. controls (431.5,166.31) and (421.09,176.5) .. (408.25,176.5) .. controls (395.41,176.5) and (385,166.31) .. (385,153.75) -- cycle ;
%Straight Lines [id:da3777742197603755] 
\draw    (331.5,152.75) -- (387.5,152.5) ;
%Straight Lines [id:da01635751939547947] 
\draw    (253.5,96.5) -- (288,142) ;
%Straight Lines [id:da6633767687204817] 
\draw    (287,165.5) -- (254.5,203.5) ;
%Straight Lines [id:da3605859970876615] 
\draw    (458.5,101.5) -- (426,139) ;
%Straight Lines [id:da9887266785867475] 
\draw    (427,168.5) -- (462.5,202.5) ;
%Right Arrow [id:dp7496461117394901] 
\draw   (477,146.88) -- (498.3,146.88) -- (498.3,142) -- (512.5,151.75) -- (498.3,161.5) -- (498.3,156.63) -- (477,156.63) -- cycle ;

% Text Node
\draw (516,143.4) node [anchor=north west][inner sep=0.75pt]    {$\cdots $};

@@

\begin{frame}
\frametitle{Spinor-helicity formalism}
    The critical point for Spinor-helicity formalism is that a 4-vector $p_\mu$ in $(\frac{1}{2},\frac{1}{2})$ representation can be equivalently represented by a bispinor in $(\frac{1}{2},0)\bigoplus (0,\frac{1}{2})$ representation.
    Specifically
    \begin{itemize}
        \item $\bm{\text{Massless Case}}$\\
    \begin{equation*}
        p_\mu \sigma^\mu=p_{\alpha\dot{\alpha}}=\begin{pmatrix*} 
            p^0-p^3 & -p^1+ip^2\\
            -p^1-ip^2 & p^0+p^3
        \end{pmatrix*}
    \end{equation*}
    And $p_{\alpha\dot{\alpha}}$ can be decomposed into product of two Weyl spinors
    \begin{equation*}
        p_{\alpha\dot{\alpha}}=\lambda_\alpha \tilde{\lambda}_{\dot{\alpha}}=\aket{\lambda}[\lambda|
    \end{equation*}
    Here we can notice that there is an ambiguity for the definition, the momentum is invariant under the following redefinition
    \begin{equation*}
        \lambda \rightarrow t^{-1}\lambda, \qquad \tilde{\lambda}\rightarrow t\tilde{\lambda}, \qquad t\in\mathbb{C^*} 
    \end{equation*}
    same as 
    \begin{equation*}
        \aket{\lambda}\rightarrow t^{-1}\aket{\lambda}, \qquad \sket{\lambda}\rightarrow t\sket{\lambda}
    \end{equation*}
    \end{itemize}
\end{frame}

\begin{frame}
    \begin{itemize}
        \item[]  This redefinition just matches the $U(1)$ little group transformation.
        \vspace{0.5em}

        The scattering amplitudes should transform covariantly under little group scaling:
        \begin{equation*}
            \color{red} \mathcal{A}_n(\{\aket{1},\sket{1},h_1\},\ldots\{t_i^{-1}\aket{i},t_i\sket{i},h_i\},\ldots )=t_i^{2h_i}\mathcal{A}_n
        \end{equation*}
        \item \textbf{Massive Case}\\
        It can also be handled in terms of spinor-helicity variable, see also 	arXiv:1709.04891 [hep-th] (Nima Arkani-Hamed, Tzu-Chen Huang, Yu-tin Huang).
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{3-point can be completely determined}
    $\bullet$ 3-particle special kinematics determines an on-shell 3-point amplitude with massless particles depends only on either angle or square brackets of the external momenta.

    Let us suppose thet it depends only on angle brackets, then we can write down the general ansatz
    \begin{equation*}
        A_3(1^{h_1},2^{h_2},3^{h_3})=c\avg{12}^{x_{12}}\avg{13}^{x_{13}}\avg{23}^{x_{23}},
    \end{equation*}
    Little group scaling tells us that
    \begin{equation*}
        t_1^{2h_1} A_3(1^{h_1},2^{h_2},3^{h_3})=ct_1^{-x_{12}}t_1^{-x_{13}}\avg{12}^{x_{12}}\avg{13}^{x_{13}}\avg{23}^{x_{23}}.
    \end{equation*}
    We can obtain
    \begin{equation*}
        2h_1=-x_{12}-x_{13}
    \end{equation*}
\end{frame}

\begin{frame}
    Similarly, we can also obtain
    \begin{equation*}
        2h_2=-x_{12}-x_{23},\qquad 2h_3=-x_{13}-x_{23}.
    \end{equation*}
    Then all index can be solved from this system of equations, so that
    \begin{equation*}
        A_3^{h_1h_2h_3}=c\avg{12}^{h_3-h_1-h_2}\avg{31}^{h_2-h_1-h_3}\avg{23}^{h_1-h_2-h_3}\quad h_1+h_2+h_3<0.
    \end{equation*}
    Also for square brackets case, we can obtain
    \begin{equation*}
        A_3^{h_1h_2h_3}=c^{'}[12]^{h_1+h_2-h_3}[23]^{h_2+h_3-h_1}[31]^{h_3+h_1-h_2}\quad h_1+h_2+h_3>0.
    \end{equation*}
    \textbf{Example}: 3-gluon amplitude\\
    \begin{equation*}
        A_3(g_1^-,g_2^-,g_3^+)=g\frac{\avg{12}^3}{\avg{23}\!\avg{31}}
    \end{equation*}
\end{frame}
\section{Introduction of quiver gauge theory}
\begin{frame}
    \frametitle{Introduction of Quiver or Moose gauge theory}
    \begin{itemize}
        \item Quiver: A container for carring arrows
        \item Moose: A kind of deer with large horns 
    \end{itemize}

@@

\begin{frame}
    \frametitle{Pure 2-site amplitude}
    \begin{itemize}
        \item $\Phi V_2 \Phi^\dagger V_1$
        \begin{equation*}
            A[1,2,3_1^+,4_2^-]=\frac{\mdavg{14}{24}}{\mdavg{13}{23}}
        \end{equation*}
        \item $\Phi V_2 \Phi^\dagger V_1V_1$
        \begin{equation*}
            A[1,2,3_1^+,4_1^+,5_2^-]=(-1)\frac{\avg{2\textcolor{green}{5}}^2\!\avg{1\textcolor{green}{5}}^2}{\textcolor{blue}{\mdavg{23}{34}\!\avg{41}}\textcolor{red}{\mdavg{25}{51}}}
        \end{equation*}
        \item $\Phi V_2V_2 \Phi^\dagger V_1V_1$
        \begin{equation*}
            A[1,2,3_1^+,4_1^+,5_2^+,6_2^-]=\frac{\avg{2\textcolor{green}{6}}^2\!\avg{1\textcolor{green}{6}}^2}{\textcolor{blue}{\mdavg{23}{34}\!\avg{41}}\!\textcolor{red}{\mdavg{25}{56}\!\avg{51}}}
        \end{equation*}

>>>>

\documentclass{beamer}
\usetheme{Madrid}
\usefonttheme{professionalfonts}
\usecolortheme{rose}
\usepackage{fontspec}
\setmainfont{Times New Roman}
\usepackage{amsmath}
\usepackage{bm}
\usepackage{booktabs}
\usepackage{tikz}
\usepackage{svg}
\usepackage{graphics}
\usepackage{appendixnumberbeamer}
\usepackage{mathtools}
\usepackage{enumitem}
\usepackage{subcaption}
\usepackage{comment}
\usepackage{slashed}
\usepackage[most]{tcolorbox}
\tcbset{
  thickitembox/.style={
    colback=white,
    colframe=white,
    left=2mm,
    before skip=4pt,
    after skip=4pt,
    borderline west={3pt}{0pt}{gray},  % ← 这里控制线条粗细和颜色
    enhanced,
  }
}
\setlist[itemize]{label=\textbullet}
\usetikzlibrary{decorations.pathreplacing}
\usetikzlibrary{arrows.meta}
\setlength{\parskip}{0.3em}
\newcommand{\aket}[1]{|#1\rangle}
\newcommand{\sket}[1]{|#1]}
\newcommand{\avg}[1]{\langle #1 \rangle}
\newcommand{\mdavg}[2]{\langle #1 \rangle\!\langle #2 \rangle}
\newcommand{\asqu}[1]{{\langle#1\rangle}^2}
\AtBeginSection[]{
\begin{frame} 
    \frametitle{Contents}
    \tableofcontents[currentsection]
\end{frame}
}
\title[Application of BCFW]{Tree level scattering amplitude in (De)constructed gauge theory}
\author{Su Yingze}
\institute{Nagoya University}
\date[4 21st 2025]{April 21st 2025}

\begin{document}
\frame{\titlepage}
\section{Why we need new method?}
\begin{frame}
    \frametitle{Why we need new method?}
    Feynman diagram is a brilliant method without doubt, but it also faces many challenges.
    \begin{itemize}
        \item How to compute high multiplicity amplitudes, like n gluons scattering.
        \item Gauge redundancies bring us many structral complications and non-physical degrees of freedom.
        \item Some symmetries are not manifest in the lagrangian level, like the dual superconformal symmetry for $\mathcal{N}=4$ SYM, etc.
        \item The unexpected simplicity of some amplitudes has led to the speculation that local QFT may not 
        be the most fundamental framework.
    \end{itemize}
\end{frame}
\begin{frame}
    \frametitle{From Frynman diagram to On-shell method}
    On-shell here means that all quantities we use are gauge invariant and satisfy the on-shell condition.
    Specifically, there are many ingredients under this frame
    \begin{itemize}
        \item The analytic continuation for S-matrix.
        \item The color-ordered amplitudes.
        \item The BCFW recursion relation.
        \item The spinor helicity discription for amplitudes.
    \end{itemize}
\end{frame}
\section{Preliminary}
\begin{frame}
    \frametitle{A brief introduction to BCFW}
    BCFW recursion relation is a method to compute scattering amplitude recursively, means that you can 
    compute higher point amplitudes from lower point.
    \par
 \begin{itemize}[label=\textbullet]
    \item Ruth Britto
    \item Freddy Cachazo
    \item Bo Feng
    \item Edward Witten
 \end{itemize}

\begin{center}

@@

 %Shape: Ellipse [id:dp47704771803228196] 
 \draw  [fill={rgb, 255:red, 158; green, 158; blue, 158 }  ,fill opacity=1 ] (179.79,126.94) .. controls (179.79,120.82) and (184.73,115.86) .. (190.81,115.86) .. controls (196.89,115.86) and (201.82,120.82) .. (201.82,126.94) .. controls (201.82,133.06) and (196.89,138.02) .. (190.81,138.02) .. controls (184.73,138.02) and (179.79,133.06) .. (179.79,126.94) -- cycle ;
 %Straight Lines [id:da8859462256956995] 
 \draw    (163,96.75) -- (182.27,118.91) ;
 %Straight Lines [id:da980370255241411] 
 \draw    (201.82,126.94) -- (232.38,126.66) ;
 %Straight Lines [id:da41368612060172827] 
 \draw    (182.82,135.52) -- (165.75,153.25) ;
 %Right Arrow [id:dp6770308298589597] 
 \draw   (240.37,124.24) -- (254.74,124.24) -- (254.74,121.68) -- (264.32,126.8) -- (254.74,131.92) -- (254.74,129.36) -- (240.37,129.36) -- cycle ;
 %Shape: Ellipse [id:dp9789947232756657] 
 \draw  [fill={rgb, 255:red, 158; green, 158; blue, 158 }  ,fill opacity=1 ] (277.26,126.94) .. controls (277.26,120.82) and (282.19,115.86) .. (288.27,115.86) .. controls (294.35,115.86) and (299.28,120.82) .. (299.28,126.94) .. controls (299.28,133.06) and (294.35,138.02) .. (288.27,138.02) .. controls (282.19,138.02) and (277.26,133.06) .. (277.26,126.94) -- cycle ;
 %Straight Lines [id:da15853752019875] 
 \draw    (263.22,98.41) -- (279.74,118.91) ;
 %Straight Lines [id:da28595275955528565] 
 \draw    (299.28,126.94) -- (329.84,126.66) ;
 %Straight Lines [id:da7505788363123894] 
 \draw    (280.29,135.52) -- (263.22,153.25) ;
 %Shape: Ellipse [id:dp870376485686725] 
 \draw  [fill={rgb, 255:red, 158; green, 158; blue, 158 }  ,fill opacity=1 ] (351.87,126.66) .. controls (351.87,120.54) and (346.94,115.58) .. (340.86,115.58) .. controls (334.77,115.58) and (329.84,120.54) .. (329.84,126.66) .. controls (329.84,132.78) and (334.77,137.74) .. (340.86,137.74) .. controls (346.94,137.74) and (351.87,132.78) .. (351.87,126.66) -- cycle ;
 %Straight Lines [id:da5791423310908868] 
 \draw    (363.43,98.97) -- (349.94,118.91) ;
 %Straight Lines [id:da5454664407915119] 
 \draw    (349.43,134.42) -- (365.28,152.14) ;
 %Right Arrow [id:dp848095583389827] 
 \draw   (368.11,124.79) -- (382.49,124.79) -- (382.49,122.23) -- (392.07,127.35) -- (382.49,132.48) -- (382.49,129.92) -- (368.11,129.92) -- cycle ;

 % Text Node
 \draw (393.76,120.95) node [anchor=north west][inner sep=0.75pt]    {$\cdots $};

 \end{tikzpicture}
\end{center}

@@

\begin{frame}
    \frametitle{Spinor-Helicity formalisim}
In the part of introduction to BCFW
\begin{figure}
    \centering
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[height=4em]{recrel1.pdf} 
    \end{minipage}
    \hspace{0.01em}
    \begin{minipage}{0.45\textwidth}
        \centering
        \(
        \vcenter{\hbox{$\rightarrow$}} \quad \text{No helicity appears here}
        \)
    \end{minipage}
\end{figure}

but the S-matrix is a function of moentum $p_i$ and helicity $h_i$
\begin{center}

%Shape: Circle [id:dp6973592945628315] 
\draw  [color={rgb, 255:red, 248; green, 0; blue, 0 }  ,draw opacity=1 ] (302.8,146.93) .. controls (302.81,142.78) and (306.18,139.44) .. (310.32,139.45) .. controls (314.47,139.46) and (317.81,142.83) .. (317.8,146.97) .. controls (317.79,151.11) and (314.42,154.46) .. (310.28,154.45) .. controls (306.14,154.44) and (302.79,151.07) .. (302.8,146.93) -- cycle ;
%Straight Lines [id:da7518027963985391] 
\draw [color={rgb, 255:red, 247; green, 18; blue, 18 }  ,draw opacity=1 ]   (310.28,154.45) -- (296.03,178.04) ;
\draw [shift={(295,179.75)}, rotate = 301.13] [color={rgb, 255:red, 247; green, 18; blue, 18 }  ,draw opacity=1 ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;

% Text Node
\draw (260.25,137.9) node [anchor=north west][inner sep=0.75pt]    {$\mathcal{M}( p_{i} ,h_{i})$};
% Text Node
\draw (173.25,181) node [anchor=north west][inner sep=0.75pt]  [font=\small,color={rgb, 255:red, 247; green, 13; blue, 13 }  ,opacity=1 ] [align=left] {How can we catch the information of helicity?};

\end{tikzpicture}
\end{center}
The answer is \textbf{Spinor-Helicity formalism} 
\(
\xrightarrow{\text{}} 
\)
Catch \(p_i\) and \(h_i\) at the same time.

\end{frame}
\begin{frame}
\frametitle{Spinor-helicity formalism}
    \begin{itemize}
        \item $\textbf{\text{Massless Case}}$\\
    \begin{equation*}
        p_\mu \sigma^\mu=p_{\alpha\dot{\alpha}}=\lambda_\alpha \tilde{\lambda}_{\dot{\alpha}}=\aket{\lambda}[\lambda|
    \end{equation*}
    There is an ambiguity for the definition, the momentum is invariant under the following redefinition
    \begin{equation*}
        \lambda \rightarrow t^{-1}\lambda, \qquad \tilde{\lambda}\rightarrow t\tilde{\lambda}, \qquad t\in\mathbb{C} 
    \end{equation*}
    same as 
    \begin{equation*}
        \aket{\lambda}\rightarrow t^{-1}\aket{\lambda}, \qquad \sket{\lambda}\rightarrow t\sket{\lambda}
    \end{equation*}
    The scattering amplitudes should transform covariantly under little group scaling:
    \begin{equation*}
        \color{red} \mathcal{A}_n(\{\aket{1},\sket{1},h_1\},\ldots\{t_i^{-1}\aket{i},t_i\sket{i},h_i\},\ldots )=t_i^{2h_i}\mathcal{A}_n
    \end{equation*}
    \end{itemize}
\vspace{-2em}
    \begin{itemize}
    \item \textbf{Massive Case}\\
    It can also be handled in terms of spinor-helicity variable, see also 	arXiv:1709.04891 [hep-th] (Nima Arkani-Hamed, Tzu-Chen Huang, Yu-tin Huang).
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{ On-shell 3-point can be completely determined}
    \textbf{On-shell 3-point for real momentum}

    Because of the constrain from momentum conservation and on-shell condition
    \begin{equation*}
        p_1=\kappa p_3, \qquad p_2=(1-\kappa)p_3 \quad(\text{Collinear})
    \end{equation*}
    All of the contribution 
    \begin{equation*}
        (p_1\cdot p_2),\quad (p_1\cdot p_3),\quad(p_2\cdot p_3)\quad =0  
    \end{equation*}
    In terms of Spinor- Helicity variable, we have 
    \begin{equation*}
        2p_1\cdot p_2=\avg{12}[21]=0\, \longrightarrow \,\avg{12}=[21]^*=0
    \end{equation*}
    \textcolor{red}{You can not obtain any notrvial thing from 3-point!}

    Of coure, you can introduce non-minimal interaction
    \begin{equation*}
        \mathcal{L}_3 \ni \frac{1}{\Lambda^2}\bar{\Psi}\slashed{D}(\Box \Psi)
    \end{equation*}
    but it still equals to 0 in the on-shell case.
\end{frame}

\begin{frame}
    \textbf{Another necessarity to introduce complex momentum}

    If the momentum is complexed, we have 
    \begin{equation*}
        \avg{12}\neq[21]^*
    \end{equation*}
    Then we can obtain
    \begin{equation*}
        \aket{1}\propto \aket{2}\propto \aket{3} \qquad or \qquad \sket{1}\propto \sket{2}\propto \sket{3}
    \end{equation*}
    It means that 3-point amplitude depends only on angle brackets or squar brackets. Here I choose the first case to give an example
    \begin{equation*}
        A_3(1^{h_1},2^{h_2},3^{h_3})=c\avg{12}^{x_{12}}\avg{13}^{x_{13}}\avg{23}^{x_{23}},
    \end{equation*}
    Little group scaling tells us that
    \begin{equation*}
        t_1^{2h_1} A_3(1^{h_1},2^{h_2},3^{h_3})=ct_1^{-x_{12}}t_1^{-x_{13}}\avg{12}^{x_{12}}\avg{13}^{x_{13}}\avg{23}^{x_{23}}.
    \end{equation*}
    We can obtain
    \begin{equation*}
        2h_1=-x_{12}-x_{13}
    \end{equation*}
    Similarly, we can also obtain
    \begin{equation*}
        2h_2=-x_{12}-x_{23},\qquad 2h_3=-x_{13}-x_{23}.
    \end{equation*}
\end{frame}

\begin{frame}
    Then all index can be solved from this system of equations, so that
    \[
    \boxed{
    \begin{aligned}
        A_3^{h_1h_2h_3} &= c\avg{12}^{h_3-h_1-h_2}\avg{31}^{h_2-h_1-h_3}\avg{23}^{h_1-h_2-h_3}
        \quad & h_1+h_2+h_3 < 0 \\[0.5em]
        A_3^{h_1h_2h_3} &= c' [12]^{h_1+h_2-h_3}[23]^{h_2+h_3-h_1}[31]^{h_3+h_1-h_2}
        \quad & h_1+h_2+h_3 > 0
    \end{aligned}
        }
    \]

    \textbf{\textcolor{red}{$\star$\,All massless 3-point ampltides are completely determined by little froup scalling!}}

    \textbf{Example}: 3-gluon amplitude\\
    \begin{equation*}
        A_3(g_1^-,g_2^-,g_3^+)=g\frac{\avg{12}^3}{\avg{23}\!\avg{31}}
    \end{equation*}
    There's another possibility 
    \begin{equation*}
        A_3(g_1^-,g_2^-,g_3^+)=g'\frac{[13][23]}{[12]^3}
    \end{equation*}
    but actually it comes from the \textcolor{red}{non-local} interaction $g'AA\frac{\partial}{\square}A$, so we discard it.
\end{frame}
\section{Introduction of quiver gauge theory}
\begin{frame}
    \frametitle{Introduction of Quiver or Moose gauge theory}
    \begin{itemize}
        \item Quiver: A container for carring arrows
        \item Moose: A kind of deer with large horns 
    \end{itemize}

@@

\begin{frame}
    \frametitle{Pure 2-site amplitude}
    \begin{itemize}
        \item $\Phi V_2 \Phi^\dagger V_1$
        \begin{equation*}
            A[1,2,3_1^+,4_2^-]=\frac{\mdavg{14}{24}}{\mdavg{13}{23}}
        \end{equation*}
        \item $\Phi V_2 \Phi^\dagger V_1V_1$
        \begin{equation*}
            A[1,2,3_1^+,4_1^+,5_2^-]=(-1)\frac{\avg{2\textcolor{green}{5}}^2\!\avg{1\textcolor{green}{5}}^2}{\textcolor{blue}{\mdavg{23}{34}\!\avg{41}}\textcolor{red}{\mdavg{25}{51}}}
        \end{equation*}
        \item $\Phi V_2V_2 \Phi^\dagger V_1V_1$
        \begin{equation*}
            A[1,2,3_1^+,4_1^+,5_2^+,6_2^-]=\frac{\avg{2\textcolor{green}{6}}^2\!\avg{1\textcolor{green}{6}}^2}{\textcolor{blue}{\mdavg{23}{34}\!\avg{41}}\!\textcolor{red}{\mdavg{25}{56}\!\avg{51}}}
        \end{equation*}       
    \end{itemize}
\end{frame}

\begin{frame}
    \begin{itemize}
        \item Compact formula for general case
        \begin{equation*}
            A=\frac{\asqu{2\textcolor{green}{a}}\!\asqu{1\textcolor{green}{a}}}{\underbrace{\avg{2\textcolor{blue}{\star}}\cdots \avg{\textcolor{blue}{\star}1}}_{SU(N_1)}\underbrace{\avg{2\textcolor{red}{\ast} }\cdots \avg{\textcolor{red}{\ast} 1}}_{SU(N_2)}}
        \end{equation*} 
        \begin{minipage}{0.7\textwidth}
            \raggedright  % 或者 \centering 或 \raggedleft
            \textcolor{green}{Green:} \,Particle with $-$ helicity\\
            \textcolor{blue}{Blue:}\, Particle belongs to the first gauge group\\
            \textcolor{red}{Red:}\, Particle belongs to the second gauge group\\
            $\star$: \,Order for gauge group 1\\
            $\ast$: \,Order for gauge group 2 
            \end{minipage}
